What do incoming university students believe about open science practices in

### 2021-03-24 analysis/Manuscript.Rmd
Updated with panel figure

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)

@@

@@

diff_fun(x = norms, y = cnorms)

@@

>>>>

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(psych) #for correlation matrices
library(tidyselect)

@@

 \@ref(tab:chunk-name)

@@

diff_fun(x = norms, y = cnorms) #throws error non-numeric argument to binary operator

@@

```{r correlation_matrix}
#pairs.panel etc. won't really work because there are too many variables
#And we only need corrs between matched pairs
#So doing this a bit more manually
layout(matrix(1:8, ncol = 4))

plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "Critical counternorm", ylab = "Critical norm")
abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))

plot(df$prereg_norm ~ jitter(df$prereg_cnorm), ylab = "Prereg norm", xlab = "Prereg counternorm")
abline(lm(df$prereg_norm ~ df$prereg_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$prereg_norm, df$prereg_cnorm),2)))

plot(df$reg_report_norm ~ jitter(df$reg_report_cnorm), ylab = "Reg Reports norm", xlab = "Reg Reports counternorm")
abline(lm(df$reg_report_norm ~ df$reg_report_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$reg_report_norm, df$reg_report_cnorm),2)))

plot(df$phack_norm ~ jitter(df$phack_cnorm), ylab = "p-hacking rnorm", xlab = "p-hacking counternorm")
#potential confusion here about direction of phrasing (pro p-hacking = counternorm?)
abline(lm(df$phack_norm ~ df$phack_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$phack_cnorm, df$phack_norm),2)))

plot(df$hark_norm ~ jitter(df$hark_cnorm), ylab = "HARKing norm", xlab = "HARKing counternorm")
abline(lm(df$hark_norm ~ df$hark_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$hark_cnorm, df$hark_norm),2)))

plot(df$info_for_rep_norm ~ jitter(df$info_for_rep_cnorm), ylab = "Replicability norm", xlab = "Replicability counternorm")
abline(lm(df$info_for_rep_norm ~ df$info_for_rep_cnorm), col = "blue")
legend(x='right', legend=paste('Cor =', round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)))

plot(df$preprint_norm ~ jitter(df$preprint_cnorm), ylab = "Preprints norm", xlab = "Preprints counternorm")
abline(lm(df$preprint_norm ~ df$preprint_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$preprint_norm, df$preprint_cnorm,
                                                       use = "pairwise.complete.obs"),2)))

plot(df$open_materials_norm ~ jitter(df$open_materials_cnorm), ylab = "Open materials norm", xlab = "Open materials counternorm")
abline(lm(df$open_materials_norm ~ df$open_materials_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_materials_norm, df$open_materials_cnorm, use = "pairwise.complete.obs"),2)))

plot(df$open_data_norm ~ jitter(df$open_data_cnorm), ylab = "Open data norm", xlab = "Open data counternorm")
abline(lm(df$open_data_norm ~ df$open_data_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_data_norm, df$open_data_cnorm),2)))

plot(df$open_access_norm ~ jitter(df$open_access_cnorm), ylab = "Open access norm", xlab = "Open access counternorm")
abline(lm(df$open_access_norm ~ df$open_access_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$open_access_norm, df$open_access_cnorm),2)))
